Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2019-02-04 AnalyticStructure_main.tex
corrected URL for the SI

% Useful packages
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,braket}
\usepackage{tikz}
\usepackage{xifthen}
%\pgfplotsset{compat=1.15}

@@

All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the supplementary information, may be found at the URL~\footnote{\texttt{https://github.com/luigigenovese/LR-nb/blob/master/ POLARIZABILITY/nb\_paper/LR\_Analysis.ipynb}, or \texttt{https://gitlab.com/luigigenovese/ localization-of-excitations/ blob/master/LR\_Analysis.ipynb}}

>>>>

% Useful packages
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,braket}
\usepackage{tikz}
\usepackage{xifthen}
\usepackage{url}
%\pgfplotsset{compat=1.15}

@@

All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the ones presented in the Supplementary Information, may be found at the URL~\footnote{\protect\url{https://github.com/luigigenovese/LR-nb/blob/master/POLARIZABILITY/nb_paper/LR_Analysis.ipynb}}

### 2019-02-04 Supplementary_material.tex
Update on Overleaf.
corrected URL for the SI

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{mathtools,braket}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}

@@

The growth of the localized sector with the number of atoms of the molecule seems thus to be a general feature.
A simple interpretation of this fact may be provided by considering perturbatively the coupling term $\op V'=0$ in Eq.~19 of the paper.
Indeed, larger molecules behave possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.
In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$. In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig. \ref{exc-land}.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amssymb,amsmath,url}
\usepackage{mathtools,braket}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}

@@

The growth of the localized sector with the number of atoms of the molecule seems thus to be a general feature.
A simple interpretation of this fact may be provided by considering perturbatively the coupling term $\op V'=0$ in Eq.~19 of the paper.
Indeed, larger molecules possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.

In a simplified two-orbitals picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is given by $\Omega_a=\epsilon_a-\epsilon_p$.
The increase of the KS DOS below the continuum threshold is therefore directly responsible of the increase of the number of localized excitations above IP.

 Such a two-orbital picture is of course not valid anymore when the coupling $\op V'$ is switched on. Yet, by interpreting perturbatively the action of the coupling term the same arguments hold true; larger molecule seem to have higher rate of  localized excitations as their DOS of KS bound states is higher.

 All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis of all the molecules considered in this study may be found at the URL~\url{https://github.com/luigigenovese/LR-nb/blob/master/POLARIZABILITY/nb_paper/LR_Analysis.ipynb}.
